---
title: "Linear and Logistic Regressions using SparkR"
author: "Hang Yuan"
date: "December 15, 2015"
output: html_document
---

We will try to run both linear and logistic regressions using SparkR. We will use a small
dataset `cats` from MASS package. Basically each entry has a gender, body weight and heart weight, but
first we will try to look a quick look at what our dataset is like.

### Dataset info
```{r}
library("MASS")
data(cats)
head(cats)
summary(cats)
```

Now we want to look at correlation between body weight and heart weight. Intuitively a larger hear weight should result in
a larger body weight. drawing the scatter-plot to have an intuition. The scatter-plot confirms the intuition.

```{r}
plot(cats$Hwt, cats$Bwt, xlab = "Heart weight", ylab = "Body weight", main = "Body weight vs Heart weight")
```

### SparkR setup
Now we need to init sparkR. We will also need sqlContext to convert the local data frame from R to DataFrame.
In an interactive shell, these two should be already created.

```{r}
Sys.setenv(SPARK_HOME= "/Users/yuancalvin/spark-1.5.2") # Set this to where sparkR is installed
.libPaths(c(file.path(Sys.getenv("SPARK_HOME"), "R", "lib"), .libPaths()))
library(SparkR)
sc <- sparkR.init(master="local")
sqlContext <- sparkRSQL.init(sc)
```

### Convert R data frame to DataFrame
DataFrame is essentially the Spark version data frame with better optimization.
Since the logistic regression doesn't muti-classification yet, we need to transform
the `M` to 1 and `F` to 0 for `sex`.
```{r}
toConvert <- function(x){
  if (x == 'F'){
     x <- 0
  } else {
    x <-1
  }
}
cats$Sex <- unlist(lapply(cats$Sex, toConvert))
# Split the data into training and test sets
library(caret)
set.seed(100)
trainIndex <- createDataPartition(cats$Sex, p = .7,
                                  list = FALSE,
                                  times = 1)
head(trainIndex)
train <- cats[trainIndex, ]
test <- cats[-trainIndex, ]

# Change F into 1 and M into 2 for logistic regression
trainDF <- SparkR::createDataFrame(sqlContext, train)
testDF <- SparkR::createDataFrame(sqlContext, test)
head(trainDF)
```

### Linear Regression
Using `SparkR::glm` is almost identical as what one would have for `glm` except that `summary()` is not yet
supported for `glm`. `ggplot` is currently not available for RDD.

```{r}
lin_spark <- SparkR::glm(Bwt ~ Hwt, data = trainDF, family = "gaussian")
predications <- SparkR::predict(lin_spark, testDF)
showDF(SparkR::select(predications, "Bwt", "prediction"))
# abline(lin_spark)
```

### Logstic Regression
Now we will run a logistic regression using sex of each cat as the dependent variable.

```{r}
model_log <- SparkR::glm(Sex ~ Bwt + Hwt, data= trainDF, family = "binomial")
predications <- SparkR::predict(model_log, testDF)
showDF(SparkR::select(predications, "Sex", "prediction"))
```


